# Sanity Check

Load the data.
```{r}
data <- read.csv("data/caravan-insurance-challenge.csv")
```

Number of rows and columns.
```{r}
dim(data)
```

Number of missing values.
```{r}
sum(is.na(data))
```
No missing values are present in the data.

According to the data description (https://www.kaggle.com/datasets/uciml/caravan-insurance-challenge) the only variables that need to be one hot encoded are the 'MOSTYPE' and 'MOSHOOFD' variables. They will be one-hot encoded just before building the models.
The 'CARAVAN' variable (response variable) belongs to the L4 encoding but it will be considered as a binary variable (0 or 1) instead of a categorical variable (0,1,2,3,...) because such variable assumes only 0,1 values.


# Train-Test Split

Perform the train-test split according to the 'ORIGIN' variable.
```{r}
train <- data[data$ORIGIN == "train", ]
test <- data[data$ORIGIN == "test", ]
```

Remove the 'ORIGIN' variable from the data, since it is not necessary anymore.
```{r}
train <- train[, -which(names(train) == "ORIGIN")]
test <- test[, -which(names(test) == "ORIGIN")]
```

```{r}
dim(train)
```
The train set has 5822 rows and 86 columns.

```{r}
dim(test)
```
The test set has 4000 rows and 86 columns.
This means that the test set includes approximately the 40% of the original data.


Save the train and test data. These sets will be denoted as raw because they have not been preprocessed yet.
```{r}
write.csv(train, "data/train_raw.csv", row.names = FALSE)
write.csv(test, "data/test_raw.csv", row.names = FALSE)
```
