---
title: "Train-Test Split"
output: html_notebook
---

```{r}
data <- read.csv("data/caravan-insurance-challenge.csv")
```
Load the data.

```{r}
dim(data)
```
Number of rows and columns.

```{r}
sum(is.na(data))
```
Number of missing values. No missing values are present in the data.

```{r}
str(data)
```
Check the data types. 
All the variables are numeric (int) except the 'ORIGIN'
variable which is a chr.
According to the data description 
(https://www.kaggle.com/datasets/uciml/caravan-insurance-challenge), all the 
variables can be thought as factors except MAANTHUI' (avg size household) and
'MEGEMOMV' (avg size hosehold).
So, we will convert all the variables to factors.

```{r}
#Convert all the variables to factors except 'MAANTHUI' and 'MGEMOMV'
for (column in names(data)) {
  if (column != "MAANTHUI" && column != "MGEMOMV") {
    data[, column] <- as.factor(data[, column])
  }
}
```

```{r}
l0_descriptions <- c(
  "High Income, expensive child", "Very Important Provincials",
  "High status seniors", "Affluent senior apartments", "Mixed seniors",
  "Career and childcare", "Dinki's (double income no kids)",
  "Middle class families", "Modern, complete families", "Stable family",
  "Family starters", "Affluent young families", "Young all american family",
  "Junior cosmopolitan", "Senior cosmopolitans", "Students in apartments",
  "Fresh masters in the city", "Single youth", "Suburban youth",
  "Etnically diverse", "Young urban have-nots", "Mixed apartment dwellers",
  "Young and rising","Young, low educated", "Young seniors in the city",
  "Own home elderly", "Seniors in apartments", "Residential elderly",
  "Porchless seniors: no front yard", "Religious elderly singles",
  "Low income catholics", "Mixed seniors", "Lower class large families",
  "Large family, employed child", "Village families",
  "Couples with teens 'Married with children'", "Mixed small town dwellers",
  "Traditional families", "Large religous families", "Large family farms",
  "Mixed rurals"
)

l1_descriptions <- c("20-30 years", "30-40 years", "40-50 years",
                     "50-60 years", "60-70 years", "70-80 years")

l2_descriptions <- c(
  "Successful hedonists", "Driven Growers", "Average Family", "Career Loners",
  "Living well", "Cruising Seniors", "Retired and Religious",
  "Family with grown ups", "Conservative families", "Farmers"
)

l3_descriptions <- c(
  "0%", "1 - 10%", "11 - 23%", "24 - 36%", "37 - 49%",
  "50 - 62%", "63 - 75%", "76 - 88%", "89 - 99%", "100%"
)

l4_descriptions <- c(
  "0", "1 - 49", "50 - 99", "100 - 199", "200 - 499",
  "500 - 999", "1000 - 4999", "5000 - 9999", "10,000 - 19,999", ">= 20,000"
)
```

Rename the levels of the variables to their corresponding labels given by the descri

```{r}
no_endoded_variables <- c("MAANTHUI", "MGEMOMV")
l0_variables <- c("MOSTYPE")
l1_variables <- c("MGEMLEEF")
l2_variables <- c("MOSHOOFD")
#l3_variables are the variables not in the list above that start with M
l3_variables <- 

```





